MSstatsPTM: Statistical relative quantification of post-translational modifications in bottom-up mass spectrometry-based proteomics

### 2022-07-07 main/MSstatsPTM_Main.tex
minor changes

\begin{eqnarray}
\Delta_{Protein} = \mu_{i} - \mu_{i^{\prime}}
\end{eqnarray}

@@

We separately visualize the PTM and global protein side by side, allowing for easier interpretation and comparison across the datasets. In the modeling stage this is further separated into PTM, global protein, and adjusted PTM visualizations. This allows users to see the affect of the adjustment.

>>>>

\begin{eqnarray}
\hat{\Delta}_{Protein} = \hat{\mu}_{i} - \hat{\mu}_{i^{\prime}}
\end{eqnarray}

@@

We include visualizations for QC and model assessment. In QC plots the PTM and global protein are shown side by side, allowing for easier interpretation and comparison across data. In the model plots this is further separated into PTM, global protein, and adjusted PTM visualizations, allowing users to see the affect of the adjustment.
